Distinction Centrality Analysis

### 2025-07-18 analysis.qmd
clique

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- add_vertices(g5, 1)
   g6 <- g6 + edge(8,1) #circle graph wit pendant
   g7 <- make_full_graph(4, directed = FALSE)
   g7 <- add_vertices(g7, 1)
   g7 <- g7 + edge(1,5)
   plot(g7)
```

```{r Toy Networks Plots}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "circle-plus-one.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "kite.png"))
   plot.graph.norm(g7, l = "kk")
   dev.off()
```

>>>>

```{r Toy Examples}
   g1 <- make_star(7, mode = "undirected") # star graph
   g2 <- g1 + edge(2,3)
   g2 <- g2 + edge(2,4)
   g2 <- g2 + edge(3,4)
   g2 <- g2 + edge(5,6)
   g2 <- g2 + edge(5,7)
   g2 <- g2 + edge(6,7) # structural fold
   g3 <- g1 + edge(2,4)
   g3 <- g3 + edge(3,4)
   g3 <- g3 + edge(5,6)
   g3 <- g3 + edge(5,7) # intra-connected clusters
   g4 <- g3 + edge(2,7) # inter-connected clusters
   g5 <- make_ring(7) #circle graph
   g6 <- add_vertices(g5, 1)
   g6 <- g6 + edge(8,1) # circle graph plus pendant
   g7 <- make_full_graph(6, directed = FALSE)
   g7 <- add_vertices(g7, 1)
   g7 <- g7 + edge(1,7) # clique plus pendant
   g8 <- make_full_graph(7, directed = FALSE) # clique
```

```{r Toy Networks Plots}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1, l = "kk")
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2, l = "kk")
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "circle-plus-one.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
   png(here("Plots", "kite.png"))
   plot.graph.norm(g7, l = "kk")
   dev.off()
   png(here("Plots", "clique.png"))
   plot.graph.norm(g8, l = "circle")
   dev.off()
```
